The {TestIdeals} package for \emph{Macaulay2}

### 2019-01-29 Fsing/TestIdealsPaper/TestIdeals.tex
Fixed a typo in the paper.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y,z];
i2 : f = y^2*z^3-x^5-2*z^5;
i3 : frobeniusPower( 10/11, ideal f )
o3 = ideal 1
o3 : Ideal of R
i5 : frobeniusPower( 120/121, ideal f )
             2        3
o6 = ideal (z , x*z, x )
o6 : Ideal of R
i7 : ((HSLGModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip

>>>>

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y,z];
i2 : f = y^2*z^3-x^5-2*z^5;
i3 : frobeniusPower( 1/11, ideal f^10 )
             2        3
o6 = ideal (z , x*z, x )
o3 : Ideal of R
i5 : frobeniusPower( 1/121, ideal f^120 )
             2        3
o6 = ideal (z , x*z, x )
o6 : Ideal of R
i7 : ((HSLGModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip
